---
title: "ggplot_theme_testing"
output: html_document
---

# Testing ggplot theme

ggplot has several useful pre-maid themes for aethetic charts which saves time creating your own theme. The following notebook generates several plots and visualises them to enable quick and easy access to what themes look like - so you don't have to plot each one each time to test them out. 

## Line plot testing

```{r}

library(tidyverse)
library(openxlsx) 
library(janitor)
library(readxl)
library(stringr)
library(rlang)
library(ggplot2)
library(ggthemes)  


`%notin%` <- Negate(`%in%`) # Custom negate function


load("data/Trade_datasets.RData")

path<-setwd(stringr::str_extract(rstudioapi::getActiveDocumentContext()$path,".+[/]")) 

# filter trade data for line plot 

df <- trade_annual %>% filter(iso2 %in% c("DE","FR","IE"))

line_plot <- 
  df %>%
  ggplot(
    aes(
      x = year,
      y = total,
      color = country
     )
    )+
  geom_line()

print(line_plot)

```

```{r}

# line plot using ggplot default 
LAB = labs(x = "Year",
       y = "Trade (£'000s)",
       title = "Total trade time-series",
       subtitle = "Top UK-EU trading partners",
       caption = "source: ONS"
  )
line_plot + LAB
  

```


### ggplot themes examples

Testing ggplot themes for a line plot

#### theme_minimal

removes axis lines and ticks. Plain white background. Light grey grid lines 

```{r}
line_plot + theme_minimal() + LAB
```

#### theme_bw

Same light formatting as theme_light but with grid border lines around entire chart and axis ticks in black. 

``` {r}

line_plot + theme_bw() + LAB


```

#### theme_classic

No grid axis lines, y, x border and tick lines in black. 

```{r}

line_plot + theme_classic() + LAB
```

#### theme_dark

dark background and grid lines - not a fan

```{r}

line_plot + theme_dark()

```

#### theme_light

All white background and light grey border, grid lines and ticks

```{r}

line_plot + theme_light() + LAB
```

#### theme_linedraw

bold black border and grid lines. 

I think this would be useful in a scatter plot where you want to closely identify where points are falling. 

```{r}

line_plot + theme_linedraw() + LAB
```

#### theme_test

Similar to theme_bw - however without grid lines

```{r}

line_plot + theme_test() + LAB

```

#### theme_void 

removes all axis, grids, borders. 

Looks good for a line plot if you want to plot a time series to identify the trend rather than values. 

```{r}

line_plot + theme_void() + LAB

```

### ggthemes library 

ggthemes adds extended pre-created ggplot themes to use. 

#### theme_clean

same as theme_classic with border around legend and dotted y-axis

```{r}

line_plot + theme_clean() + LAB

````

#### theme_economist

```{r}

line_plot + theme_economist() + LAB

```

#### theme_excel_new 

```{r}
line_plot + theme_excel_new() + LAB

```

#### theme_fivethirtyeight 

good looking theme for line plot and increases title size and legend underneath graph

```{r}
line_plot + theme_fivethirtyeight() + LAB
```

#### theme_gdocs

overall light graph which also decreases the alpha of the plots

```{r}
line_plot + theme_gdocs() + LAB

```

#### theme_wsj

Decent formatting for linechart to identify trends. 
Issue being veyr large title and legend title

```{r}

line_plot + theme_wsj()

```


#### theme_tufte


```{r}

line_plot + theme_tufte() + LAB

```

#### theme_stata

Teal blue background around plot. Centered title and border around legend. 

```{r}

line_plot + theme_stata() + LAB
```


#### theme_hc 


```{r}


line_plot + theme_hc() + LAB

```


#### theme_few


```{r}

line_plot + theme_calc() + LAB

```


#### theme_map

Good theme for overall trend plot as has additional title formatting and legend positioning 

```{r}

line_plot + theme_map() +LAB
```

#### theme_solarized

Different background colouring which might be of interest to people 

```{r}

line_plot + theme_solarized() + LAB

```

```{r}

line_plot + theme_foundation() + LAB

```


### ggtheme color scales 

ggthemes provides custom color scales for creating mroe aesthetic graphs. 

The following section will test select few ones on simple line chart. 

Line plot will be updated to reflect 6 countries. 

```{r}
df <- trade_annual %>% filter(iso2 %in% c("DE","FR","IE","NL","SE","ES"))

line_plot <- 
  df %>%
  ggplot(
    aes(
      x = year,
      y = total,
      color = country
     )
    )+
  geom_line(size=1)

```


#### scale_colour_wsj


```{r}

line_plot + theme_wsj()+ scale_colour_wsj("colors6")
```

```{r}
line_plot + theme_calc()+ scale_colour_calc()

```
