---
title: "ggplot_theme_testing"
output: html_document
---

# Testing ggplot theme

ggplot has several useful pre-maid themes for aethetic charts which saves time creating your own theme. The following notebook generates several plots and visualises them to enable quick and easy access to what themes look like - so you don't have to plot each one each time to test them out. 

## Line plot testing

```{r}

library(tidyverse)
library(openxlsx) 
library(janitor)
library(readxl)
library(stringr)
library(rlang)
library(ggplot2)
library(ggthemes)  


`%notin%` <- Negate(`%in%`) # Custom negate function


load("data/Trade_datasets.RData")

path<-setwd(stringr::str_extract(rstudioapi::getActiveDocumentContext()$path,".+[/]")) 

# filter trade data for line plot 

df <- trade_annual %>% filter(iso2 %in% c("DE","FR","IE"))

line_plot <- 
  df %>%
  ggplot(
    aes(
      x = year,
      y = total,
      color = country
     )
    )+
  geom_line()

print(line_plot)

```

```{r}

# line plot using ggplot default 
LAB = labs(x = "Year",
       y = "Trade (£'000s)",
       title = "Total trade time-series",
       subtitle = "Top UK-EU trading partners",
       caption = "source: ONS"
  )
line_plot + LAB
  

```


### ggplot themes examples

Testing ggplot themes for a line plot

#### theme_minimal

removes axis lines and ticks. Plain white background. Light grey grid lines 

```{r}
line_plot + theme_minimal() + LAB
```

#### theme_bw

Same light formatting as theme_light but with grid border lines around entire chart and axis ticks in black. 

``` {r}

line_plot + theme_bw() + LAB


```

#### theme_classic

No grid axis lines, y, x border and tick lines in black. 

```{r}

line_plot + theme_classic() + LAB
```

#### theme_dark

dark background and grid lines - not a fan

```{r}

line_plot + theme_dark()

```

#### theme_light

All white background and light grey border, grid lines and ticks

```{r}

line_plot + theme_light() + LAB
```

#### theme_linedraw

bold black border and grid lines. 

I think this would be useful in a scatter plot where you want to closely identify where points are falling. 

```{r}

line_plot + theme_linedraw() + LAB
```

#### theme_test

Similar to theme_bw - however without grid lines

```{r}

line_plot + theme_test() + LAB

```

#### theme_void 

removes all axis, grids, borders. 

Looks good for a line plot if you want to plot a time series to identify the trend rather than values. 

```{r}

line_plot + theme_void() + LAB

```

### ggthemes library 

ggthemes adds extended pre-created ggplot themes to use. 




